---
title: "WEB ANALYTICS"
author: "K srihari sasanka"
date: "2024-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
getwd()
```

```{r}
library(readxl)
df = read_excel('C:\\Users\\kandu\\OneDrive\\Documents\\R\\1555058318_internet_dataset.xlsx')
```
```{r}
(df)
```

```{r}
#q1 
#Basic understanding of the dataset and to prepare for further analysis
dim(df)
names(df)
summary(df)
```


```{r}
#q2
#So the team needs to know whether the unique page view value depends on visits.
cor(df$Uniquepageviews,df$Visits)
```
```{r}
# Example with additional customization
plot(df$Uniquepageviews, df$Visits, 
     xlab = "Unique Pageviews", 
     ylab = "Visits", 
     main = "Scatter Plot between Unique Pageviews and Visits",
     col = "blue",    # Color of points
     pch = 16,        # Point type
     xlim = c(0, 100), # X-axis limits
     ylim = c(0, 500)  # Y-axis limits
     )

```

#both are highly positively correlated,and linear trend.
#So the team can conclude that unique page values depend on 




```{r}
#q3
#Find out the probable factors from the dataset, which could affect the exits.
value_counts <- table(df$Exits)
print(value_counts)
```
```{r}
library(AER)
```
```{r}
poisson_model <- glm(Exits ~ Visits + Timeinpage, data = df, family = "poisson")


```
```{r}
dispersion_test_result <- dispersiontest(poisson_model, alternative = "greater")

```
```{r}
print(dispersion_test_result)

```
```{r}
# Print the result of the dispersion test
print(dispersion_test_result)

# Check if the p-value is less than a significance level (e.g., 0.05)
if (dispersion_test_result$p.value < 0.05) {
  cat("There is evidence of overdispersion. Consider using Negative Binomial Regression.\n")
} else {
  cat("No evidence of overdispersion. Poisson Regression may be appropriate.\n")
}

```
```{r}
summary(poisson_model)
```
Conclusions...
# a one-unit increase in 'Visits' is associated with an estimated 12.64% increase in the rate of 'Exits'.
#Visits has very less impact on exits
#a one-unit increase in 'Timeonpage' is associated with an estimated 14.23% decrease in the rate of 'Exits'.
#Timeonpage need to be increased to decrese the percentage of exits


```{r}
#q4
#Find the variables which possibly have an effect on the time on page.
model <- lm(Timeinpage  ~ Visits , data = df)
summary(model)

```
```{r}
library(ggplot2)
ggplot(df, aes(x = Continent, y = Timeinpage, fill = Continent)) +
  geom_bar(stat = "identity") +
  labs(title = "Bar Plot of Timeinpage by Continent",
       x = "Continent",
       y = "Timeinpage") +
  theme_minimal()

```

#Visits are more important,also people from North america has more no of visits,has shown greater influence to increase the time on page.

```{r}
#q5.Factors that are impacting the bounce.
model <- glm( Bounces ~ Visits + Timeinpage , data = df, family = "poisson")
```
```{r}
library(car)
vif(model)

```
#VIF values are less than 5 ,so considerable,if i consider Uniquepageviews the vif will be high,because Visits,Pageview are highly correlated
```{r}
summary(model)
```
#Final Conclusion for Web Data Analysis
#same like Exits,Bounces can be reduced by increasing the timeonpage,that is done by recommending relevant information and making website attrative and easily accessible and userfriendly.


